Importance of Sampling Frequency in the Dynamic Speckle Analysis

### 2019-03-26 article/article_1.tex
trucomanx-formulation

The dynamic speckle analysis over biological samples has become  currently  an important
study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
to determine the level of biological activity. 
The importance of technical aspects of dynamic speckle analysis,
as the stability of laser illumination level, was analized \cite{gonzalez2018diode}; 
and was showed as indexes as
the absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
by the variation of illumination level. Thus, It is necessary analyze the effect
of technical parameters that affect the perceived illumination level; In these sense
analyze the effect of sampling frequency in a dynamic speckle analysis

@@

In this work were presented comparisons of behavior of three dynamic speckle indexes
subject to different values of sampling frequency, thus we concluded that:
It is important to know to choose an appropriate sampling frequency, 
being recommendable to use the minimal sampling frequency possible to get an acceptable maximum excursion,
so that the phenomenon under study to be in the analyzed frequency band.
Finally, 
we show that the digitization  of speckle signal imply a restriction of frequency 
band of signal and consequently this affect the result of an speckle analysis.

>>>>

The dynamic laser speckle analysis has become in the last years  an important
study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
to determine the  activity level of biological materials. 
The importance of technical aspects of dynamic laser speckle analysis,
as the stability of laser illumination level has been  analyzed \cite{gonzalez2018diode}; 
and also It was studed as indexes,
as absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
by the variation of illumination level. Thus, It is necessary analyze the effect
of technical parameters that affect the perceived illumination level; In these sense
we analyze the effect of sampling frequency in a dynamic laser speckle analysis.

@@

In this work were presented comparisons of behavior of three dynamic laser speckle indexes
subject to different values of sampling frequency, thus we concluded that:
It is important to know to choose an appropriate sampling frequency, 
being recommendable to use the minimal sampling frequency possible to get an acceptable maximum excursion,
so that the phenomenon under study to be in the analyzed frequency band.
Finally, 
we show that the digitization  of speckle signal imply a restriction of frequency 
band of signal and consequently this affect the result of an speckle analysis.
